### 2022-03-07 manuscript.tex
add figures [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/cb15eaa36551642a3015ab49949d551fc56653b6.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/cb15eaa36551642a3015ab49949d551fc56653b6/checks
https://github.com/scherzerthesis/thesis/actions/runs/1948373378

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/ffcdd549f7ffe6f12407e950146e88869af4f04d/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/ffcdd549f7ffe6f12407e950146e88869af4f04d}{scherzerthesis/thesis@ffcdd54}
on March 4, 2022.

@@

@@

Expression of BRAF\textsuperscript{V600E} in the distal epithelium of the mouse lung elicits clonal tumorigenic outgrowths of alveolar type 2 (AT2) pneumocytes (Dankort et al.~2007).Prior work has shown that \emph{Trp53\textsuperscript{fl/fl}} cooperates with BRAF(V600E) to form malignant lung tumors when Cre recombinase is activated (Dankort \emph{et al.}, 2007; Shai \emph{et al.}, 2015). Therefore, we compared the tumor burden of \emph{Braf\textsuperscript{Cat/+}} mice with either p53 loss (\emph{Trp53\textsuperscript{fl/fl}}, p53\textsuperscript{R172H} (\emph{Trp53\textsuperscript{R172H/R172H}}), or p53\textsuperscript{R245W} (\emph{Trp53\textsuperscript{R245W/R245W}}) after infection with 106 pfu of adenovirus expressing surfactant protein C specific Cre (ad5-Spc-Cre) (Figure \ref{fig:01} A). As expected, mice developed lung cancer, consistent with previous findings (Figure \ref{fig:01} B-C). However, there was a striking, highly reproducible increase in the tumor size of tumors harboring \emph{Trp53\textsuperscript{R172H/R172H}} and to a lesser extent \emph{Trp53\textsuperscript{R245W/R245W}}, compared to \emph{Trp53\textsuperscript{fl/fl}} (Figure \ref{fig:01} B-D). These data led us to hypothesize that p53\textsuperscript{R172H} and p53\textsuperscript{R245W} expression alters tumor progression uniquely from p53 deletion, and these differences may be potentially evident of gain-of-function effects imparted by mutant-53. Since lung cancer patients with mutations in \emph{TP53} often start only have one mutated \emph{p53} allele unless loss of heterozygosity (LOH) occurs. Therefore, we generated mice heterozygous for both \emph{Braf\textsuperscript{CAT}} and either \emph{Trp53\textsuperscript{fl}} , \emph{Trp53\textsuperscript{R172H}}, or \emph{Trp53\^{} R245W\^{}} and observed their survival over time (Figure \ref{fig:01} E). We noted that \emph{Trp53\textsuperscript{R172H/+}} mice had diminished median overall survival compared to \emph{Trp53\textsuperscript{fl/+}} mice (183 days and 216 days), with \emph{Trp53\textsuperscript{R245W/+}} mice falling in between the two groups (median survival 212 days) (Figure \ref{fig:01} E).

We observed a distinct separation of survival between mice harboring lung tumors that are either \emph{Trp53\textsuperscript{fl/+}}, \emph{Trp53\textsuperscript{R172H/+}}, and \emph{Trp53\textsuperscript{R245W/+}}, this separation is diminished when altered p53 alleles are homozygous (Figure \ref{fig:01} F). \emph{Trp53\textsuperscript{R172H/R172H}} mice have a median survival of 120 days while \emph{Trp53\textsuperscript{fl/fl}} mice have a median survival of 136 days. Importantly, this observed difference in survival is statistically significant (Log-rank test p\textless{} 0.001) and is likely a reflection of worse diseased, characterized by enhanced tumor burden and tumor size.

@@

Increased malignancy in lung adenocarcinoma is often associated with altered states of tumor cell identity and dedifferentiation (van Veen \emph{et al.}, 2019; Marjanovic \emph{et al.}, 2020). Since LUADs often arise from AT2 cells, we surveyed the expression of AT2 cell identifiers, such as NKX2-1, a master regulator of AT2 transcriptional programs, and SPC, a marker of differentiated AT2 cells (Marjanovic \emph{et al.}, 2020). Quantification of over 50 tumors from \emph{Braf\textsuperscript{V600E/+}} mice with either \emph{Trp53\^{} flfl\^{}}, \emph{Trp53\textsuperscript{R172H/R172H}}, and \emph{Trp53\textsuperscript{R245W/R245W}} revealed that \emph{Trp53\textsuperscript{R172H/R1722H}} mice had significantly more tumors that stained negative for NKX2-1 and SPC (Figure \ref{fig:02} A an B). This finding strongly indicates that mutant-p53 tumors are dedifferentiated. Since HMGA2 expression is associated with LUAD dedifferentiation and worse patient prognosis, we performed IHC for HMGA2 (Cite). We noted an increase in HMGA2-positive tumors in both \emph{Trp53\textsuperscript{R172H/R172H}}, and \emph{Trp53\textsuperscript{R245W/R245W}} tumors compared to \emph{Trp53\textsuperscript{fl/fl}} (Figure \ref{fig:02} A,B). Thus, this data taken together reveals that Trp53R172H/R172H mice exhibit both a higher tumor burden and worse overall survival than \emph{Trp53\textsuperscript{fl/fl}}, but the tumors developed in these mice are more likely to exhibit malignant progression and dedifferentiation.

One striking feature of lung tumors in mice either heterozygous or homozygous for \emph{Trp53 \textsuperscript{R172H}} or \emph{Trp53\textsuperscript{R245W}} is how few tumors and tumor cells have detectable levels of mutant-p53 protein as measured by Immunohistochemistry (IHC). One critical aspect of normal p53 function is self-regulation through transcriptional activation of its negative regulator MDM2 (Wu \emph{et al.}, 1993). Thus, we predicted that homozygous p53 mutant-cells would exhibit increased mutant-p53 protein. Interestingly, in our models, we observed mutant p53 protein accumulation is restricted to malignant cells exhibited by lack of papillary architecture and nuclear atypia (Figure \ref{fig:02} C). Indeed, p53 immunostaining is correlated with increased phospho-ERK1/2 detection (Figure \ref{fig:02} D). Moreover, immunofluorescence of p53 and its positive regulator, p19/ARF, reveal cells with high p19/ARF are also high in p53 accumulation (Figure \ref{fig:02} D). This result suggests that even in homozygous mutant\_Trp53\_ mice, there is still a barrier to mutant-p53 accumulation, and our data suggests that elevated levels of p19/ARF is important for mutant-p53 accumulation, even with homozygous p53 mutations. Collectively, these data indicate that \emph{Trp53\textsuperscript{R172H}} drives more aggressive lung adenocarcinoma formation in BRAF(V600E) driven mouse models of lung cancer.

@@

Given that previous research has determined that p53 mutations can confer resistance to both chemotherapies and pathway-targeted therapies (Rusch \emph{et al.}, 1995; Huang \emph{et al.}, 2011), we next questioned whether our p53 alterations would be sufficient to drive therapeutic resistance in BRAF\textsuperscript{V600E}-driven cell lines exposed to pathway-targeted therapeutics commonly administered to BRAF\textsuperscript{V600E} mutant patients, such as the combination of dabrafenib (BRAFi) plus trametinib (MEKi) (Planchard \emph{et al.}, 2016). Cell lines were derived from \emph{Braf\textsuperscript{CAT/+}} murine tumors expressing either \emph{Trp53\textsuperscript{flfl}}, \emph{Trp53\textsuperscript{R172H/R172H}}, or \emph{Trp53\textsuperscript{R245W/R245W}}) 14 weeks after infection with ad5-Spc-Cre. Cell lines expressing either \emph{Trp53\textsuperscript{R172H/R172H}} or \emph{Trp53\textsuperscript{R245W/R245W}} were completely resistant to single agent dabrafenib and resistant to the combination of dabrafenib plus trametinib (Figure \ref{fig:03} A,B). Of note, \emph{Trp53\textsuperscript{R172H/R172H}} and \emph{Trp53\textsuperscript{R245W/R245W}} cell lines express increased ERK1/2 activity, as evidenced by increased phosphorylated ERK1/2, both with and without Dabrafenib and Trametinib (Figure \ref{fig:03} E). Moreover, \emph{Trp53\textsuperscript{R172H/R172H}} mice retain a larger tumor burden after a week 4 treatment of MAPK blockade \emph{in vivo} (Figure \ref{fig:03} E). To gain relevance to human lung cancer, we infected BRAF(V600E) mutant HCC364 cells with lentivirus expressing human cancer hotspot mutant p53\textsuperscript{R175H}. p53\textsuperscript{R175H} expressing cells were more proliferative and more refractory than parental HCC364 cells (Figure \ref{fig:03} F and G).Collectively, these \emph{in vitro} and \emph{in vivo} data suggest missense mutant p53\textsuperscript{R175H} and its murine homologue p53\textsuperscript{R172H}, as well as p53\textsuperscript{R245W} can support cancer cell viability in the face of BRAF+MEK blockade that cannot be achieved by p53-null mutations.

@@

Due to our observations that mutant p53\textsuperscript{R172H} drives more aggressive cancer phenotypes such as increased growth, dedifferentiation, and resistance to FDA-approved therapeutics, we reasoned that this would be reflected in a change in the transcriptional landscape. This is due in part, by the transcriptional trans-activation potential by mutant p53. RNA sequencing of cell lines generated from p53-mutant mouse lung tumors do reveal transcriptomic differences between both p53\textsuperscript{R172H} and p53\textsuperscript{R245W} cells compared to p53-null cell lines (Figure \ref{fig:04} 4 A). Interestingly, genes involved in cell cycle regulation, epithelial-to-mesenchymal transition (EMT), and MYC pathway are upregulated in both p53\textsuperscript{R172H} and p53\textsuperscript{R2245W} cell lines (Figure 4 \ref{fig:04} B). These results suggest that mutant-p53 is affecting transcription of genes involved in pro-growth signaling pathways.

\begin{figure}
\hypertarget{fig:01}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/figure1_021022.svg}
\caption{\textbf{Differential BRAF\textsuperscript{V600E} lung tumorigenesis imparted by p53-Hotspot mutants.} \textbf{(A)} Genetically-engineered alleles of \emph{Braf\textsuperscript{v600E}} and \textsuperscript{Trp53} before and after Cre-Recombinase. \textbf{(B)} Tumor burden and \emph{(C)}** Tumor size of BRAF(V600E) plus Trp53-wildtype, null, or mutant alleles 14 weeks post Cre-mediated recombination. \emph{(D)} Representative H\&E images 14 weeks after Cre-recombination. \textbf{(E)} Survival of mice with Heterozygous \emph{Trp53} mutant alleles. \textbf{(F)} Survival of mice with homozygous \emph{Trp53} alleles.}\label{fig:01}
}
\end{figure}

\begin{figure}
\hypertarget{fig:02}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/figure2_021722.svg}
\caption{\textbf{Missense mutant-p53 alters lung adenocarcinoma differentiation status and accumulation of mutant-p53 correlates with p19 ARF expression.} \textbf{(A)} Panel representative IHC sections stained with SPC,NKX2-1, p53 and HMGA2. \textbf{(B)} H-score of individual tumors. \textbf{(C)} Association between mutant-p53 R172H accumulation and increased malignancy and dedifferentiation. \textbf{(D)} serial section of P53-HI and pERK1/2-HI tumors compared to adjacent low. \textbf{(E)} Colocalization of p19/ARF and p53 in p53-mutant tumors}\label{fig:02}
}
\end{figure}

\begin{figure}
\hypertarget{fig:03}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/figure3_021722.svg}
\caption{\textbf{Mutant-p53 cell lines are refractory to BRAFi+MEKi.} \textbf{(A)} Response of GEMMs to BRAFi+MEKi chow after four weeks \textbf{(B)} in vitro dose response to BRAFi single agent. \textbf{(C)} in vitro timecourse with dabrafenib (1000nm) plus trametinib (100nM). \textbf{(D)} Accumulation of dead cells in dabrafenib plus trametinib measured by CytotoxRed accumulation. \textbf{(E)} Immunoblotting of phospho-ERK1/2 in response to dabrafenib plus trametinib. \textbf{(F)} Ectopic expression of p53\textsuperscript{R17H} in human HCC364 cells. \textbf{(E)} Response of p53\textsuperscript{R175H} cells to dabrafenib plus trametinib.}\label{fig:03}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/figure4_021722.svg}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:04}
}
\end{figure}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/cb15eaa36551642a3015ab49949d551fc56653b6/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/cb15eaa36551642a3015ab49949d551fc56653b6}{scherzerthesis/thesis@cb15eaa}
on March 7, 2022.

@@

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tubaseq_figure1.svg}
\caption{\textbf{Differential BRAF\textsuperscript{V600E} lung tumorigenesis imparted by p53-Hotspot mutants.} \textbf{(A)} Genetically-engineered alleles of \emph{Braf\textsuperscript{v600E}} and \textsuperscript{Trp53} before and after Cre-Recombinase. \textbf{(B)} Tumor burden and \emph{(C)}** Tumor size of BRAF(V600E) plus Trp53-wildtype, null, or mutant alleles 14 weeks post Cre-mediated recombination. \emph{(D)} Representative H\&E images 14 weeks after Cre-recombination. \textbf{(E)} Survival of mice with Heterozygous \emph{Trp53} mutant alleles. \textbf{(F)} Survival of mice with homozygous \emph{Trp53} alleles.}\label{fig:06}
}
\end{figure}

@@

Expression of BRAF\textsuperscript{V600E} in the distal epithelium of the mouse lung elicits clonal tumorigenic outgrowths of alveolar type 2 (AT2) pneumocytes (Dankort et al.~2007).Prior work has shown that \emph{Trp53\textsuperscript{fl/fl}} cooperates with BRAF(V600E) to form malignant lung tumors when Cre recombinase is activated (Dankort \emph{et al.}, 2007; Shai \emph{et al.}, 2015). Therefore, we compared the tumor burden of \emph{Braf\textsuperscript{Cat/+}} mice with either p53 loss (\emph{Trp53\textsuperscript{fl/fl}}, p53\textsuperscript{R172H} (\emph{Trp53\textsuperscript{R172H/R172H}}), or p53\textsuperscript{R245W} (\emph{Trp53\textsuperscript{R245W/R245W}}) after infection with 106 pfu of adenovirus expressing surfactant protein C specific Cre (ad5-Spc-Cre) (Figure \ref{fig:11} A). As expected, mice developed lung cancer, consistent with previous findings (Figure \ref{fig:11} B-C). However, there was a striking, highly reproducible increase in the tumor size of tumors harboring \emph{Trp53\textsuperscript{R172H/R172H}} and to a lesser extent \emph{Trp53\textsuperscript{R245W/R245W}}, compared to \emph{Trp53\textsuperscript{fl/fl}} (Figure \ref{fig:11} B-D). These data led us to hypothesize that p53\textsuperscript{R172H} and p53\textsuperscript{R245W} expression alters tumor progression uniquely from p53 deletion, and these differences may be potentially evident of gain-of-function effects imparted by mutant-53. Since lung cancer patients with mutations in \emph{TP53} often start only have one mutated \emph{p53} allele unless loss of heterozygosity (LOH) occurs. Therefore, we generated mice heterozygous for both \emph{Braf\textsuperscript{CAT}} and either \emph{Trp53\textsuperscript{fl}} , \emph{Trp53\textsuperscript{R172H}}, or \emph{Trp53\^{} R245W\^{}} and observed their survival over time (Figure \ref{fig:11} E). We noted that \emph{Trp53\textsuperscript{R172H/+}} mice had diminished median overall survival compared to \emph{Trp53\textsuperscript{fl/+}} mice (183 days and 216 days), with \emph{Trp53\textsuperscript{R245W/+}} mice falling in between the two groups (median survival 212 days) (Figure \ref{fig:11} E).

We observed a distinct separation of survival between mice harboring lung tumors that are either \emph{Trp53\textsuperscript{fl/+}}, \emph{Trp53\textsuperscript{R172H/+}}, and \emph{Trp53\textsuperscript{R245W/+}}, this separation is diminished when altered p53 alleles are homozygous (Figure \ref{fig:11} F). \emph{Trp53\textsuperscript{R172H/R172H}} mice have a median survival of 120 days while \emph{Trp53\textsuperscript{fl/fl}} mice have a median survival of 136 days. Importantly, this observed difference in survival is statistically significant (Log-rank test p\textless{} 0.001) and is likely a reflection of worse diseased, characterized by enhanced tumor burden and tumor size.

@@

Increased malignancy in lung adenocarcinoma is often associated with altered states of tumor cell identity and dedifferentiation (van Veen \emph{et al.}, 2019; Marjanovic \emph{et al.}, 2020). Since LUADs often arise from AT2 cells, we surveyed the expression of AT2 cell identifiers, such as NKX2-1, a master regulator of AT2 transcriptional programs, and SPC, a marker of differentiated AT2 cells (Marjanovic \emph{et al.}, 2020). Quantification of over 50 tumors from \emph{Braf\textsuperscript{V600E/+}} mice with either \emph{Trp53\^{} flfl\^{}}, \emph{Trp53\textsuperscript{R172H/R172H}}, and \emph{Trp53\textsuperscript{R245W/R245W}} revealed that \emph{Trp53\textsuperscript{R172H/R1722H}} mice had significantly more tumors that stained negative for NKX2-1 and SPC (Figure \ref{fig:12} A an B). This finding strongly indicates that mutant-p53 tumors are dedifferentiated. Since HMGA2 expression is associated with LUAD dedifferentiation and worse patient prognosis, we performed IHC for HMGA2 (Cite). We noted an increase in HMGA2-positive tumors in both \emph{Trp53\textsuperscript{R172H/R172H}}, and \emph{Trp53\textsuperscript{R245W/R245W}} tumors compared to \emph{Trp53\textsuperscript{fl/fl}} (Figure \ref{fig:12} A,B). Thus, this data taken together reveals that Trp53R172H/R172H mice exhibit both a higher tumor burden and worse overall survival than \emph{Trp53\textsuperscript{fl/fl}}, but the tumors developed in these mice are more likely to exhibit malignant progression and dedifferentiation.

One striking feature of lung tumors in mice either heterozygous or homozygous for \emph{Trp53 \textsuperscript{R172H}} or \emph{Trp53\textsuperscript{R245W}} is how few tumors and tumor cells have detectable levels of mutant-p53 protein as measured by Immunohistochemistry (IHC). One critical aspect of normal p53 function is self-regulation through transcriptional activation of its negative regulator MDM2 (Wu \emph{et al.}, 1993). Thus, we predicted that homozygous p53 mutant-cells would exhibit increased mutant-p53 protein. Interestingly, in our models, we observed mutant p53 protein accumulation is restricted to malignant cells exhibited by lack of papillary architecture and nuclear atypia (Figure \ref{fig:12} C). Indeed, p53 immunostaining is correlated with increased phospho-ERK1/2 detection (Figure \ref{fig:12} D). Moreover, immunofluorescence of p53 and its positive regulator, p19/ARF, reveal cells with high p19/ARF are also high in p53 accumulation (Figure \ref{fig:12} D). This result suggests that even in homozygous mutant\_Trp53\_ mice, there is still a barrier to mutant-p53 accumulation, and our data suggests that elevated levels of p19/ARF is important for mutant-p53 accumulation, even with homozygous p53 mutations. Collectively, these data indicate that \emph{Trp53\textsuperscript{R172H}} drives more aggressive lung adenocarcinoma formation in BRAF(V600E) driven mouse models of lung cancer.

@@

Given that previous research has determined that p53 mutations can confer resistance to both chemotherapies and pathway-targeted therapies (Rusch \emph{et al.}, 1995; Huang \emph{et al.}, 2011), we next questioned whether our p53 alterations would be sufficient to drive therapeutic resistance in BRAF\textsuperscript{V600E}-driven cell lines exposed to pathway-targeted therapeutics commonly administered to BRAF\textsuperscript{V600E} mutant patients, such as the combination of dabrafenib (BRAFi) plus trametinib (MEKi) (Planchard \emph{et al.}, 2016). Cell lines were derived from \emph{Braf\textsuperscript{CAT/+}} murine tumors expressing either \emph{Trp53\textsuperscript{flfl}}, \emph{Trp53\textsuperscript{R172H/R172H}}, or \emph{Trp53\textsuperscript{R245W/R245W}}) 14 weeks after infection with ad5-Spc-Cre. Cell lines expressing either \emph{Trp53\textsuperscript{R172H/R172H}} or \emph{Trp53\textsuperscript{R245W/R245W}} were completely resistant to single agent dabrafenib and resistant to the combination of dabrafenib plus trametinib (Figure \ref{fig:13} A,B). Of note, \emph{Trp53\textsuperscript{R172H/R172H}} and \emph{Trp53\textsuperscript{R245W/R245W}} cell lines express increased ERK1/2 activity, as evidenced by increased phosphorylated ERK1/2, both with and without Dabrafenib and Trametinib (Figure \ref{fig:13} E). Moreover, \emph{Trp53\textsuperscript{R172H/R172H}} mice retain a larger tumor burden after a week 4 treatment of MAPK blockade \emph{in vivo} (Figure \ref{fig:13} E). To gain relevance to human lung cancer, we infected BRAF(V600E) mutant HCC364 cells with lentivirus expressing human cancer hotspot mutant p53\textsuperscript{R175H}. p53\textsuperscript{R175H} expressing cells were more proliferative and more refractory than parental HCC364 cells (Figure \ref{fig:13} F and G).Collectively, these \emph{in vitro} and \emph{in vivo} data suggest missense mutant p53\textsuperscript{R175H} and its murine homologue p53\textsuperscript{R172H}, as well as p53\textsuperscript{R245W} can support cancer cell viability in the face of BRAF+MEK blockade that cannot be achieved by p53-null mutations.

@@

Due to our observations that mutant p53\textsuperscript{R172H} drives more aggressive cancer phenotypes such as increased growth, dedifferentiation, and resistance to FDA-approved therapeutics, we reasoned that this would be reflected in a change in the transcriptional landscape. This is due in part, by the transcriptional trans-activation potential by mutant p53. RNA sequencing of cell lines generated from p53-mutant mouse lung tumors do reveal transcriptomic differences between both p53\textsuperscript{R172H} and p53\textsuperscript{R245W} cells compared to p53-null cell lines (Figure \ref{fig:14} 4 A). Interestingly, genes involved in cell cycle regulation, epithelial-to-mesenchymal transition (EMT), and MYC pathway are upregulated in both p53\textsuperscript{R172H} and p53\textsuperscript{R2245W} cell lines (Figure 4 \ref{fig:14} B). These results suggest that mutant-p53 is affecting transcription of genes involved in pro-growth signaling pathways.

\begin{figure}
\hypertarget{fig:11}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/figure1_021022.svg}
\caption{\textbf{Differential BRAF\textsuperscript{V600E} lung tumorigenesis imparted by p53-Hotspot mutants.} \textbf{(A)} Genetically-engineered alleles of \emph{Braf\textsuperscript{v600E}} and \textsuperscript{Trp53} before and after Cre-Recombinase. \textbf{(B)} Tumor burden and \emph{(C)}** Tumor size of BRAF(V600E) plus Trp53-wildtype, null, or mutant alleles 14 weeks post Cre-mediated recombination. \emph{(D)} Representative H\&E images 14 weeks after Cre-recombination. \textbf{(E)} Survival of mice with Heterozygous \emph{Trp53} mutant alleles. \textbf{(F)} Survival of mice with homozygous \emph{Trp53} alleles.}\label{fig:11}
}
\end{figure}

\begin{figure}
\hypertarget{fig:12}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/figure2_021722.svg}
\caption{\textbf{Missense mutant-p53 alters lung adenocarcinoma differentiation status and accumulation of mutant-p53 correlates with p19 ARF expression.} \textbf{(A)} Panel representative IHC sections stained with SPC,NKX2-1, p53 and HMGA2. \textbf{(B)} H-score of individual tumors. \textbf{(C)} Association between mutant-p53 R172H accumulation and increased malignancy and dedifferentiation. \textbf{(D)} serial section of P53-HI and pERK1/2-HI tumors compared to adjacent low. \textbf{(E)} Colocalization of p19/ARF and p53 in p53-mutant tumors}\label{fig:12}
}
\end{figure}

\begin{figure}
\hypertarget{fig:13}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/figure3_021722.svg}
\caption{\textbf{Mutant-p53 cell lines are refractory to BRAFi+MEKi.} \textbf{(A)} Response of GEMMs to BRAFi+MEKi chow after four weeks \textbf{(B)} in vitro dose response to BRAFi single agent. \textbf{(C)} in vitro timecourse with dabrafenib (1000nm) plus trametinib (100nM). \textbf{(D)} Accumulation of dead cells in dabrafenib plus trametinib measured by CytotoxRed accumulation. \textbf{(E)} Immunoblotting of phospho-ERK1/2 in response to dabrafenib plus trametinib. \textbf{(F)} Ectopic expression of p53\textsuperscript{R17H} in human HCC364 cells. \textbf{(E)} Response of p53\textsuperscript{R175H} cells to dabrafenib plus trametinib.}\label{fig:13}
}
\end{figure}

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/figure4_021722.svg}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}
